### 2010-12-06 report/report.tex
Intro done?

\section{Introduction}
% Motivate and abstractly describe the problem you are addressing and
% how you are addressing it. What is the problem? Why is it important?
% What is your basic approach? A short discussion of how it fits into % related work in the area is also desirable. Summarize the basic results
% and conclusions that you will present.

This paper presents a comparison of varied learning methods to
design a gait for a quadruped robot. Using these methods we have
created walks that are several times faster than the original
hand-tuned gait.

A video presentation of this project should be viewed at

http://www.youtube.com/watch?v=ODoiOj9DdGg.
\edit{write this}

>>>>

\section{Introduction}

% Motivate and abstractly describe the problem you are addressing and
% how you are addressing it. What is the problem? Why is it important?
% What is your basic approach? A short discussion of how it fits into
% % related work in the area is also desirable. Summarize the basic
% results and conclusions that you will present.

Applications of walking robots often call for the ability to walk as
quickly, efficiently, or with as little power as possible.  Often
these optimizations are done manually by an expert who designs and
tweaks a gait specifically for a given objective.  Other groups have
used learning methods to generate gaits optimized for some metric.
Approaches differ in their starting assumptions, some essentially
tweaking the parameters of a hand-tuned model \cite{chernova}, others
exploring a reasonably compact parameter space \cite{kohl}, and still
others beginning with few assumptions besides periodicity
\cite{zykov}.

We aimed to strike a middle ground between these approaches.  Our
motion generator did not relying on hand-tweaked gaits, but it did use
a parameterized gait which, by its nature, imposes some assumptions on
the answers produced.  From this model, we used machine learning to
design a gait for a quadruped robot.

This paper presents a comparison of varied learning methods to design
a gait for a quadruped robot. Using these methods we have created
walks that are several times faster than the original hand-tuned gait.
We invite readers with short attention spans to view a video of some
of our results online here:

\url{http://www.youtube.com/watch?v=ODoiOj9DdGg}

%The code so far consists of the robot class, optimization class,
%parameterized model, sine model, and camera feedback.

\edit{proofread}
